\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-10 paper/paper.tex
intro first draft

Censorship circumvention still important
-More countries blocking
-Existing countries blocking more

Existing circumvention strategies on shaky ground
-domain fronting going away
-active probing of existing proxies
-Cenosrs fingerprinting known protocols

Importance of Refraction Networking
-what it is, how it solves many of the above problems
-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far

Challenges remain in Tapdance:
-Censor can fingerprint decoy sites
-Decoys themselves are limited (e.g. a few dozen in many cases)
-Can't have long-lived connections (performance and observability issue)
-Other performance limits (upload limit, TCP window size)

Dark decoys solve these issues
-Create new decoys from ``dark'' (unused) address space
-Clients register (via TapDance-like or other robust protocol (email, blockchain, whatever))
-Connect to custom IP address, talk whatever protocol client/station agrees on

One-time use address advantages:
-Censor cannot actively probe ahead of time (especially in IPv6), making it hard to fingerprint
-Decoys are now virtually unlimited (or limited only by address space)
-Connection can live as long as we want
-No pesky TCP/TapDance-y limits

Requirements/Challenges
-Censor can't be able to distinguish between dark decoy and legitimate hosts
    (otherwise they block all dark decoys)
    -Includes active probing: censor shouldn't be able to register existing IP
-Disruption avoidence: Want to pickup even for used addresses
    -Otherwise, censor probes to find truly unused address space and blocks
    -But can't disrupt legitimate services
    -Can overcome by limiting pickup to the registering client (but spoofing challenges...)
    -Note: also likely solved by the client-sends-SNI in the Mask site application...

>>>>

%Censorship circumvention still important
%-More countries blocking
%-Existing countries blocking more
Internet censorship continues to hamper social progress throughout the world.
Over half of the global Internet population
now live in countries that block political, social, or religious content
online~\cite{fotn2018} as governments continue to expand their censorship
policies and programs.

%Existing circumvention strategies on shaky ground
%-domain fronting going away
%-active probing of existing proxies
%-Cenosrs fingerprinting known protocols
Meanwhile, strategies to circumvent censorship using proxies have suffered many
recent setbacks. Many previously popular proxies are no longer functional due to
censors evolving new ways to block them~\cite{ensafi-tor,great-cannon},
or because they rely on temperamental
infrastructure. For example, domain fronting was a popular circumvention
strategy used by meek (in Tor), as well as the Signal secure messaging app to
get around censorship in countries it was
blocked~\cite{domain-fronting,signal,signal-domain-fronting}.
But in May~2018, Google and Amazon made both technical and policy changes to
their cloud infrastructures that removed support for domain
fronting~\cite{aws-front}. While meek
continues to use other cloud providers that (for now) continue to allow domain
fronting, Signal abandoned the strategy altogether~\cite{signal-back-on-front}.
%Combined with censors' constant improvements in discovery and blocking
%techniques~\cite{ensafi-tor,great-cannon}, ...

%Importance of Refraction Networking
%-what it is, how it solves many of the above problems
%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
One emerging technique is Refraction Networking (also known as ``Decoy
Routing''), which places proxies at cooperating Internet Service Providers
(ISPs) outside censoring countries~\cite{refraction-site}. Clients access the
proxies by connecting to unblocked ``decoy'' sites such that the packets pass by
the ISP proxy, which intercepts and injects responses as the decoy site.
Censors cannot easily block access without also blocking
legitimate connections to the decoy sites, which may be costly for the censor.
However, deploying such schemes in practice is more difficult than existing proxies:
convincing ISPs to deploy proxies in their production network is a significant
operational hurdle. To date, only one of six Refraction
Networking schemes has been deployed in practice by a large ISP:
TapDance~\cite{tadance}, a
Refraction Networking protocol that removes the need for inline
flow-blocking~\cite{frolov2017isp}.

%Challenges remain in Tapdance:
%-Censor can fingerprint decoy sites
%-Decoys themselves are limited (e.g. a few dozen in many cases)
%-Can't have long-lived connections (performance and observability issue)
%-Other performance limits (upload limit, TCP window size)
But in order to be deployed, TapDance makes an aggressive tradeoff
between observability by censors for the sake of ease of deployment.
For instance, TapDance's passive ``on the side'' architecture
does not resist active probing attacks, where the censor can send packets that
confirm whether or not a suspected connection is indeed a TapDance connection.
The use of real-world decoy sites also presents practical problems: If
decoys are limited or not particularly important, it may be easy for a
censor to block them altogether without much collateral damage. In addition, 
TapDance has several performance limitations due to its interaction with
real decoys. For example, TapDance clients' individual connection duration and upload
capacities are limited due to the interaction with the decoy's TCP and TLS stack
behavior. This forces TapDance to multiplex long-lived proxy connections over
several repeated shorter-duration decoy connections, which increases overhead and may
produce a connection pattern that is visible to censors.

%Dark decoys solve these issues
%-Create new decoys from ``dark'' (unused) address space
%-Clients register (via TapDance-like or other robust protocol (email, blockchain, whatever))
%-Connect to custom IP address, talk whatever protocol client/station agrees on
In this paper, we present Dark Decoys, a new Refraction Networking protocol that
solves these issues, while maintaining the easy-to-deploy model of TapDance
(i.e. a passive network tap). In our scheme, clients register new fictitious
decoys in the ``dark'' or unused address space of the deploying ISP. Once
registered, clients can connect to these dark decoy IP addresses as if they were
real hosts. The ISP station acts as the other end of these connections, and responds as
if it were a legitimate site or service. To the censor, these dark decoys appear
as legitimate sites or services, and even active probes won't reveal
information that would allow the censor to block them.

%One-time use address advantages:
%-Censor cannot actively probe ahead of time (especially in IPv6), making it hard to fingerprint
%-Decoys are now virtually unlimited (or limited only by address space)
%-Connection can live as long as we want
%-No pesky TCP/TapDance-y limits
Dark decoys are cheap to create, allowing for discardable \textbf{one-time use}
addresses to be used by clients. This greatly increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
can detect 90\% of dark decoys does not significantly increase the cost to the
circumvention system, giving dark decoys an advantage in the censor/circumventor
cat-and-mouse game.
We support both IPv4 and IPv6 dark decoys, though we note they are especially
powerful in IPv6 where censors cannot exhaustively scan ahead of time to
identify addresses that change behavior.
Because we fully control the server side, dark decoy connections can live as
long as needed, without the upload or timing limits faced by TapDance.

%TODO:
%Requirements/Challenges
%-Censor can't be able to distinguish between dark decoy and legitimate hosts
%    (otherwise they block all dark decoys)
%    -Includes active probing: censor shouldn't be able to register existing IP
%-Disruption avoidence: Want to pickup even for used addresses
%    -Otherwise, censor probes to find truly unused address space and blocks
%    -But can't disrupt legitimate services
%    -Can overcome by limiting pickup to the registering client (but spoofing challenges...)
%    -Note: also likely solved by the client-sends-SNI in the Mask site application...

% We implement it, it works...
We implement our dark decoy protocol under the same model as TapDance using
only a passive tap at an ISP. Furthermore, our protocol also works with
asymmetric routing (i.e. when the tap can only see packets from but not to the
client). We test our deployment on a 10~Gbps real-world ISP testbed similar to the
TapDance deployment~\cite{frolov2017isp}, and evaluate the performance and
observability compared to TapDance.
